Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-05 robdml.tex
tex

Adversarial robustness is important for DML applications.
%
In this paper, we improve the efficiency of adversarial training of DML
through HM.
%
Since regular training and the min-max adversarial training can be expressed as
two boundary cases as HM, Graduate Adversary is modeled as an ``intermediate
hardness'' the two cases, and is effective.
%
Enforcing the previously neglected Intra-Class Structure can further improve 
model robustness and adversarial training efficiency.
%
Our method outperforms previous methods.

>>>>

Adversarial robustness is crucial for DML applications.
%
In this paper, we improve adversarial training efficiency through HM.
%
Since regular training and the min-max adversarial training can be expressed as
two boundary cases of HM, Graduate Adversary has been demonstrated effective as
an ``intermediate point'' between the two cases.
%
Enforcing the previously neglected Intra-Class Structure can further improve
model robustness and adversarial training efficiency.
%
Our method outperforms previous methods.
